---
title: "CCA permutation test in ESTRA samples"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
  html_notebook:
    toc: true
    toc_float: true
---


```{r}
rm(list=ls())

library(CCA)
library(CCP)
library(foreach)
library(doParallel)


```

```{r}

df<- read.csv('G:/kings backup/Research/ED_project/documents/Lauren_CCA_2022/Psychiatry Research 2023 05/CCA redo 05 2023/IMAGEN - STRATIFY MASTER remove 2 HC no overlap.csv', as.is = TRUE)


```

## CCA on AN and HC

### get complete data
```{r}

AN_personalities <- c('neur_mean_r' ,'extr_mean_r', 'open_mean_r',  'agre_mean_r', 'cons_mean_r',  'AS_r', 'H_r' ,'IMP_r' ,'SS_r')

AN_symptoms <- c('AN_New_Girls' , 'MINI_A_MDEC', 'MINI_O_GADC', 'MINI_C_SRC')

dfCompAN <- df[ c('Usercode',AN_personalities, AN_symptoms)]
dfCompAN <- dfCompAN[complete.cases(dfCompAN), ]


```

### Canonical correlations

These values match those from STATA exactly.  

```{r}

cca_res_AN<- CCA::cc(dfCompAN[,AN_personalities] , dfCompAN[,AN_symptoms] )

print(data.frame(round(cca_res_AN$cor,4)))

```

### Permutation for CCA analysis on AN and HC

```{r}
set.seed(20240409)
p.perm(dfCompAN[,AN_personalities] , dfCompAN[,AN_symptoms], nboot = 10000, rhostart = 1, type = "Wilks")
```
Excluding the biggest canonical correlation:  
```{r}
set.seed(20240409)
p.perm(dfCompAN[,AN_personalities] , dfCompAN[,AN_symptoms], nboot = 10000, rhostart = 2, type = "Wilks")
```

Excluding the first 2 canonical correlation:  
```{r}
set.seed(20240409)
p.perm(dfCompAN[,AN_personalities] , dfCompAN[,AN_symptoms], nboot = 10000, rhostart = 3, type = "Wilks")
```

Excluding the first 3 canonical correlation:  
```{r}
set.seed(20240409)
p.perm(dfCompAN[,AN_personalities] , dfCompAN[,AN_symptoms], nboot = 10000, rhostart = 4, type = "Wilks")

```

## CCA on BN and HC

### get complete data for BN and HC
```{r}

BN_personalities <- c('neur_mean_r' ,'extr_mean_r', 'open_mean_r',  'agre_mean_r', 'cons_mean_r',  'AS_r', 'H_r' ,'IMP_r' ,'SS_r')

BN_symptoms <- c('BN_New_Girls' , 'MINI_A_MDEC', 'MINI_O_GADC', 'MINI_C_SRC')

dfCompBN <- df[ c('Usercode',BN_personalities, BN_symptoms)]
dfCompBN <- dfCompBN[complete.cases(dfCompBN), ]


```

### Canonical correlations

These values match those from STATA exactly.  

```{r}

cca_res_BN<- CCA::cc(dfCompBN[,BN_personalities] , dfCompBN[,BN_symptoms] )

print(data.frame(round(cca_res_BN$cor,4)))

```


### permutation for analysis on BN and HC


```{r}
set.seed(20240409)
p.perm(dfCompBN[,BN_personalities] , dfCompBN[,BN_symptoms], nboot = 10000, rhostart = 1, type = "Wilks")
```
Excluding the biggest canonical correlation:  
```{r}
set.seed(20240409)
p.perm(dfCompBN[,BN_personalities] , dfCompBN[,BN_symptoms], nboot = 10000, rhostart = 2, type = "Wilks")
```

Excluding the first 2 canonical correlation:  
```{r}
set.seed(20240409)
p.perm(dfCompBN[,BN_personalities] , dfCompBN[,BN_symptoms], nboot = 10000, rhostart = 3, type = "Wilks")
```

Excluding the first 3 canonical correlation:  
```{r}
set.seed(20240409)
p.perm(dfCompBN[,BN_personalities] , dfCompBN[,BN_symptoms], nboot = 10000, rhostart = 4, type = "Wilks")

```


